## Contoso

Contoso is a synthetic dataset containing sample sales transaction data for the fictional "Contoso" company. It includes various supporting tables for business intelligence, such as customer, store, product, and currency exchange data.

This dataset is perfect for practicing time series analysis, financial modeling, or any business intelligence-related tasks.

The package comes with the following datasets:

- **sales**:
  - Contains information about sales transactions, including the total sales amount, customer, store, and product involved.

- **customer**:
  - Contains details about customers, such as customer key, name, address, and demographic information.

- **store**:
  - Contains information about stores, including store key, name, location, and related details.

- **product**:
  - Contains information about products, such as product key, name, category, and price.

- **fx**:
  - Contains foreign exchange rate data, mapping currency pairs to their exchange rates on specific dates.

- **date**:
  - Contains date-related information, including date, week, month, quarter, and year for use in time-based analysis.

- **orders**:
  - Contains information about individual orders, including order key, customer key, order date, and store information.

- **orderrows**:
  - Contains detailed line items for each order, including product key, quantity, and price for each item in the order.
  
  
Built into the package is the 10K row version of the dataset. 

Using `view()`, you can see the columns' label using the [labelled](https://larmarange.github.io/labelled/index.html) package.^[Inspiration from [Crystal Lewis](https://cghlewis.com/blog/dict_clean/) excellent blog post].


If you want a larger dataset, there is also 100K, 1M, 10M and 100M which can be created with `create_contoso_duckdb()` function.
  
This will create a local duckdb database and attach the specified row size version from a motherduck database into your local database. 



The data is originally sourced from the [sqlbi](https://github.com/sql-bi/Contoso-Data-Generator-V2-Data/releases/tag/ready-to-use-data) github site 

### Dataset overview 


![Contoso](man/figures/contoso.svg)



The relationship keys that join each of the tables are listed below.

```{r}
#| echo: false
#| eval: true
#| label: keys
#| message: true
#| error: false
#| warning: false
#| width: 8

tibble::tibble(
    sales=c("order_key", "customer_key","store_key","product_key","currency_code")
    ,customer=c(NA,"customer_key",NA,NA,NA)
    ,product=c(NA,NA,NA,"product_key",NA)
    ,store=c(NA,NA,"store_key",NA,NA)
    ,order=c("order_key","customer_key","store_key" ,NA,NA)
    ,orderrows=c("order_key",NA,NA,"product_key",NA)
    ,fx=c(NA,NA,NA,NA,"from_currency")
) |> 
    tidyr::replace_na(list(sales="",customer="",product="",store="",order="",orderrows="",fx="")) |> 
    tinytable::tt() 

```

### Installation

You can install the development version of package from [GitHub](https://github.com/alejandrohagan/contoso) with:

```{r}
#| eval: false
# install.packages("pak")
pak::pak("alejandrohagan/contoso")
```

### Example

Example of how to create a duckdb database with Contoso tables loaded is below:


```{r}
#| eval: false
#| label: create-contoso-duckdb

library(contoso)

# Creates a list of DuckDB database containing Contoso datasets
contoso_db <- create_contoso_duckdb(dir = "temp",size = "1m")

# Access the sales dataset from the database
sales_data <- contoso_db$sales

```


